---
title: "ESM 204 Assignment 4 - Technical Appendix"
author: "Bridget Gibbons, BR Hoover"
date: "6/6/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(janitor)
library(stargazer)
```

```{r, include=FALSE}
#read in data

carbon <- read_csv("HW4Data.csv") %>%
  clean_names()

```

###1. Marginal Costs of Abatement for Sectors A, B, C, and D.

```{r, include = FALSE}

carbon_tidy <- gather(carbon, sector, mc, mc_a:mc_d) %>%
  mutate(sector = case_when(
    sector == "mc_a" ~ "Sector A",
    sector == "mc_b" ~ "Sector B",
    sector == "mc_c" ~ "Sector C",
    sector == "mc_d" ~ "Sector D"
  ))

#use regression to determine marginal cost of abatement
lm_a <- lm(data = carbon, mc_a ~ abatement) 
summary(lm_a)
# mc_a = -8.64448 + 0.57684*abatement

lm_b <- lm(data = carbon, mc_b ~ abatement) 
summary(lm_b)
# mc_b = 9.31770 + 0.19874*abatement

lm_c <- lm(data = carbon, mc_c ~ abatement) 
summary(lm_c)
# mc_c = -11.65503 + 0.78383*abatement

lm_d <- lm(data = carbon, mc_d ~ abatement) 
summary(lm_d)
# mc_d = 9.68751 + 0.25993*abatement

#store the slopes and intercepts for abatement curve
slope_a <- lm_a$coefficients[2]
slope_b <- lm_b$coefficients[2]
slope_c <- lm_c$coefficients[2]
slope_d <- lm_d$coefficients[2]

intercept_a <- lm_a$coefficients[1]
intercept_b <- lm_b$coefficients[1]
intercept_c <- lm_c$coefficients[1]
intercept_d <- lm_d$coefficients[1]
```

```{r, echo = FALSE}
## plot the data and regression models for each sector

ggplot(data = carbon_tidy, aes(x=abatement, y = mc)) + geom_point() +
  geom_smooth(method="lm", se = FALSE) +
  facet_wrap(~sector, scales = "free") +
  theme_light() +
  labs(x = "Abatement (tons)", y = "Marginal Cost", title = "Marginal Cost of Carbon Abatement") 
```

Marginal Cost of Abatement Functions: 

- $$MC_A= -8.65 + 0.58(Abatement)$$
- $$MC_B= 9.32 + 0.2 (Abatement)$$
- $$MC_C = -11.66 + 0.78 (Abatement)$$
- $$MC_D = 9.69 + 0.26 (Abatement)$$

The marginal cost of abatement for each sector was determined using linear regression models.

###2. Demand Curves for Carbon Emissions for Sectors A, B, C, and D 

```{r, include = FALSE}
#make dataframe columns for abatement, carbon emissions A, MB_A, carbon emissions B, MB_B, carbon emissions C, MB_C, carbon emissions D, MB_D

abatement <- seq(0,300,10)

emissions_A <- seq(180,0, -10)
marg_benefit <- merge(abatement, emissions_A, by = "row.names", all = TRUE) %>%
  select(-Row.names) %>%
  rename(abatement = x, emissions_A = y) %>%
  arrange(abatement)

emissions_B <- seq(200, 0, -10)
marg_benefit <- merge(marg_benefit, emissions_B, by = "row.names", all = TRUE) %>%
  select(-Row.names) %>%
  rename(emissions_B = y) %>%
  arrange(abatement)

emissions_C <- seq(220, 0 , -10)
marg_benefit <- merge(marg_benefit, emissions_C, by = "row.names", all = TRUE) %>%
  select(-Row.names) %>%
  rename(emissions_C = y) %>%
  arrange(abatement)

emissions_D <- seq(300, 0 , -10)
marg_benefit <- merge(marg_benefit, emissions_D, by = "row.names", all = TRUE) %>%
  select(-Row.names) %>%
  rename(emissions_D = y) %>%
  arrange(abatement)

#make the demand function for a 
demand_A_fn <- function(x){
  slope_a*(x) + intercept_a #180 is the x intercept, has the same slope because it is just the inverse 
}

#evalute demand function at each value for emissions_A
abatement_A <- seq(0,180, 10)
demand_A <- demand_A_fn(abatement_A) 
marg_benefit <- merge(marg_benefit, demand_A, by = "row.names", all = TRUE) %>%
  select(-Row.names) %>%
  rename(demand_A = y) %>%
  arrange(abatement)
#95.2 is the y intercept 

demand_B_fn <- function(x){
  slope_b*(x) + intercept_b
}
abatement_B <- seq(0,200,10)
demand_B <- demand_B_fn(abatement_B)
marg_benefit <- merge(marg_benefit, demand_B, by = "row.names", all = TRUE) %>%
  select(-Row.names) %>%
  rename(demand_B = y) %>%
  arrange(abatement)

demand_C_fn <- function(x){
  slope_c*(x) + intercept_c
}
abatement_C <- seq(0,220,10)
demand_C <- demand_C_fn(abatement_C)
marg_benefit <- merge(marg_benefit, demand_C, by = "row.names", all = TRUE) %>%
  select(-Row.names) %>%
  rename(demand_C = y) %>%
  arrange(abatement)

demand_D_fn <- function(x){
  slope_d*(x) + intercept_d
}
abatement_D <- seq(0,300,10)
demand_D <- demand_D_fn(abatement_D)
marg_benefit <- merge(marg_benefit, demand_D, by = "row.names", all = TRUE) %>%
  select(-Row.names) %>%
  rename(demand_D = y) %>%
  arrange(abatement)
```

```{r, echo = FALSE}
#plot
par(mfrow=c(2,2)) 
plot(marg_benefit$emissions_A, marg_benefit$demand_A, main = "Sector A", xlab = "Carbon Emissions (tons)", ylab = "Marginal Benefit ($/ton)", type = "l", col = "red")
plot(marg_benefit$emissions_B, marg_benefit$demand_B, main = "Sector B", xlab = "Carbon Emissions (tons)", ylab = "Marginal Benefit ($/ton)", type = "l", col = "orange")
plot(marg_benefit$emissions_C, marg_benefit$demand_C, main = "Sector C", xlab = "Carbon Emissions (tons)", ylab = "Marginal Benefit ($/ton)", type = "l", col = "green")
plot(marg_benefit$emissions_D, marg_benefit$demand_D, main = "Sector D", xlab = "Carbon Emissions (tons)", ylab = "Marginal Benefit ($/ton)", type = "l", col = "blue")
```

Demand for emission functions:
$$Demand_A = -0.58(Emissions) + 95.19 $$
$$Demand_B = -0.2(Emissions) + 49.07 $$
$$Demand_C =-0.78(Emissions) + 160.79 $$
$$Demand_D = -0.26 (Emissions)+ 87.67 $$

Sector C has the highest willingnesss to pay for the first unit of carbon emissions at $160.79 per ton. 

The demand curves are related to the previously calculated marginal benefit functions. The level at which each sector is currently emitting carbon is the point at which the marginal benefit of emitting the next ton of carbon is 0. Using that relationship, the slope and intercepts of the demand curves can be calculated.
 
###3. Country X needs to cut emissions by half, to 300 total tons

```{r, include = FALSE}
#cap on carbon

#save y intercepts for demand curves 
demand_a_int <- marg_benefit$demand_A[marg_benefit$abatement == 180]
demand_b_int <- marg_benefit$demand_B[marg_benefit$abatement == 200]
demand_c_int <- marg_benefit$demand_C[marg_benefit$abatement == 220]
demand_d_int <- marg_benefit$demand_D[marg_benefit$abatement == 300]

marg_benefit_ag <- data.frame(marg_benefit_pollution = seq(161, 0 , -1)) %>%
  mutate(emissions_A = ifelse(
    marg_benefit_pollution <= demand_a_int, (demand_a_int - marg_benefit_pollution)/slope_a, 0 
    ), 
    emissions_B = ifelse(
    marg_benefit_pollution <= demand_b_int, (demand_b_int - marg_benefit_pollution)/slope_b, 0 
    ), 
    emissions_C = ifelse(
    marg_benefit_pollution <= demand_c_int, (demand_c_int - marg_benefit_pollution)/slope_c, 0 
    ), 
    emissions_D = ifelse(
    marg_benefit_pollution <= demand_d_int, (demand_d_int - marg_benefit_pollution)/slope_d, 0 
    )) %>%
  mutate(ag_country_X = emissions_A + emissions_B + emissions_C)

#emissions Sector A
em_A_fn <- function(price){
  -price/slope_a + demand_a_int/slope_a
  
}
em_slope_a <- -1/slope_a
em_int_a <- demand_a_int/slope_a

#emissions Sector B
em_B_fn <- function(price){
  -price/slope_b + demand_b_int/slope_b
  
}
em_slope_b <- -1/slope_b
em_int_b <- demand_b_int/slope_b

#emissions Sector C
em_C_fn <- function(price){
  -price/slope_c + demand_c_int/slope_c
  
}
em_slope_c <- -1/slope_c
em_int_c <- demand_c_int/slope_c

#emissions Sector D
em_D_fn <- function(price){
  
  -price/slope_d + demand_d_int/slope_d
}
em_slope_d <- -1/slope_d
em_int_d <- demand_d_int/slope_d

#Aggregate emissions 
em_slope_ag <- em_slope_a+em_slope_b+em_slope_c
em_int_ag <- em_int_a + em_int_b + em_int_c
em_ag_fn <- function(price){
  price*em_slope_ag + em_int_ag
  
}
price_slope_ag <- function(emissions){
  -em_int_ag/em_slope_ag + emissions/em_slope_ag
  
} 
tax <- price_slope_ag(300)
#39.42658
```

####3a. Cap on carbon emissions in which each sector needs to reduce by 100 units
```{r, include = FALSE}
#cap on carbon part a 
demand_A_fn_fixed <- function(x){
  -slope_a*(x) + demand_a_int 
}
demand_B_fn_fixed <- function(x){
  -slope_b*(x) + demand_b_int 
}
demand_C_fn_fixed <- function(x){
  -slope_c*(x) + demand_c_int 
}

polluted_units_C <- 120 #polluted units for sector C
polluted_units_B <- 100 #polluted units for sector B
polluted_units_A <- 80 #polluted units for sector A

abated_units_A <- 100 #abated units for sector A
abated_units_B <- 100 #abated units for sector B
abated_units_C <- 100 #abated units for sector C

#Sector A (no tax)
pollution_benefit_A <- 80*demand_A_fn_fixed(80) + 0.5*(demand_a_int - demand_A_fn_fixed(80))*80
#5769.071
total_benefit_A <- integrate(demand_A_fn_fixed, 0 , 180)$value
abatement_cost_A <- total_benefit_A - pollution_benefit_A
#2019.762 

#Sector B (no tax)
pollution_benefit_B <- 100*demand_B_fn_fixed(100) + 0.5*(demand_b_int - demand_B_fn_fixed(100))*100
#3912.934
total_benefit_B <- integrate(demand_B_fn_fixed, 0 , 200)$value
abatement_cost_B <- total_benefit_B - pollution_benefit_B
#1925.491 

##Sector C (no tax)
pollution_benefit_C <- 120*demand_C_fn_fixed(120) + 0.5*(demand_c_int - demand_C_fn_fixed(120))*120
#13650.87 
total_benefit_C <- integrate(demand_C_fn_fixed, 0 , 220)$value
abatement_cost_C <- total_benefit_C - pollution_benefit_C
#2753.63 

# Aggregated Costs and Benefits
abatement_cost_aggregated <- abatement_cost_A + abatement_cost_B + abatement_cost_C
#6698.883

pollution_benefit_aggregated <- pollution_benefit_A + pollution_benefit_B + pollution_benefit_C
#23332.87 
```

```{r, echo = FALSE}
par(mfrow=c(2,2)) 
plot(marg_benefit_ag$ag_country_X, marg_benefit_ag$marg_benefit_pollution, main = "Country X Aggregated Marginal Benefits", xlab = "Carbon Emissions (Tons)", ylab = "Marginal Benefit ($/Ton)", type = "l", col = "red")
plot(marg_benefit$emissions_A, marg_benefit$demand_A, main = "Sector A", xlab = "Carbon Emissions (Tons)", ylab = "Marginal Benefit ($/Ton)", type = "l", col = "green")
plot(marg_benefit$emissions_B, marg_benefit$demand_B, main = "Sector B", xlab = "Carbon Emissions (Tons)", ylab = "Marginal Benefit ($/Ton)", type = "l", col = "blue")
plot(marg_benefit$emissions_C, marg_benefit$demand_C, main = "Sector C", xlab = "Carbon Emissions (Tons)", ylab = "Marginal Benefit ($/Ton)", type = "l", col = "orange")
```

```{r, echo = FALSE}
plot(marg_benefit_ag$ag_country_X, marg_benefit_ag$marg_benefit_pollution, main = "Country X Aggregated Marginal Benefits", xlab = "Carbon Emissions (Tons)", ylab = "Marginal Benefit ($/Ton)", type = "l", col = "red")
lines(marg_benefit$emissions_A, marg_benefit$demand_A, main = "Sector A", xlab = "Carbon Emissions (Tons)", ylab = "Marginal Benefit ($/Ton)", type = "l", col = "green")
lines(marg_benefit$emissions_B, marg_benefit$demand_B, main = "Sector B", xlab = "Carbon Emissions (Tons)", ylab = "Marginal Benefit ($/Ton)", type = "l", col = "blue")
lines(marg_benefit$emissions_C, marg_benefit$demand_C, main = "Sector C", xlab = "Carbon Emissions (Tons)", ylab = "Marginal Benefit ($/Ton)", type = "l", col = "orange")
abline(h=tax, lty= 2)
```

With a cap on carbon emissions, Sector A will emit 80 tons of carbon, Sector B will emit 100 tons, and Sector C will emit 120 tons. Each sector will abate 100 tons of carbon as mandated.

The cost of abatement for Sector A is 2,019.76, for Sector B is 1925.491, and for Sector C is 2,753.63. The total cost of meeting the cap of 300 tons of carbon emissions within Country X is 6,698.88. As the policy is simply a cap on emissions without an associated tax, there is no tax revenue generated.

Knowing that each sector needs to reduce its carbon emissions by 100 tons, it was possible to determine the amount that would each sector would need to abate. The total cost of abatement is the area under the marginal cost of abatement curve up to the total units that are abated. The benefit to the sector of still being able to emit some carbon is the area under the demand curve up to the total emitted units.

####3b. Tax on Carbon 

```{r, include = FALSE}
#3b 
polluted_units_C_tax <- em_C_fn(tax) #polluted units for sector C
#154.830468933185 

polluted_units_B_tax <- em_B_fn(tax) #polluted units for sector B
#48.5044240323858 

polluted_units_A_tax <- em_A_fn(tax) #polluted units for sector A
#96.6651070344293

abated_units_A_tax <- (intercept_a - tax)/ -slope_a #abated units for sector A
#83.3348929655707 

abated_units_B_tax <- (intercept_b - tax)/ -slope_b #abated units for sector B
#151.495575967614 

abated_units_C_tax <- (intercept_c - tax)/ -slope_c #abated units for sector C
#65.169531066815 

#A NUMBERS WITH TAX
pollution_benefit_A_tax <- polluted_units_A_tax*tax + 0.5*polluted_units_A_tax*(demand_a_int-tax)
#6506.221 
total_benefit_A_tax <- integrate(demand_A_fn, 0 , 180)$value
#7788.833
abatement_cost_A_tax <- total_benefit_A - pollution_benefit_A
#1282.612 

#B NUMBERS WITH TAX
pollution_benefit_B_tax <- polluted_units_B_tax*tax + 0.5*polluted_units_B_tax*(demand_b_int-tax)
#2146.154
total_benefit_B_tax <- integrate(demand_B_fn, 0 , 200)$value
#5838.426
abatement_cost_B_tax <- total_benefit_B - pollution_benefit_B
#3692.271 

##C NUMBERS W TAX
pollution_benefit_C_tax <- polluted_units_C_tax*tax + 0.5*polluted_units_C_tax*(demand_c_int-tax)
#15499.57
total_benefit_C_tax <- integrate(demand_C_fn, 0 , 220)$value
#16404.5
abatement_cost_C_tax <- total_benefit_C - pollution_benefit_C
#904.9294 

#Aggregated Costs and Benefits:
abatement_cost_aggregated_tax <- abatement_cost_A_tax + abatement_cost_B_tax + abatement_cost_C_tax
#5879.812

pollution_benefit_aggregated_tax <- pollution_benefit_A + pollution_benefit_B + pollution_benefit_C
#24151.94 

tax_revenue_A <- tax*polluted_units_A_tax
#3811.175

tax_revenue_B <- tax*polluted_units_B_tax
#1912.364 

tax_revenue_C <- tax*polluted_units_C_tax
#6104.436

tax_revenue <- tax_revenue_A + tax_revenue_B + tax_revenue_C
#11827.97
```

If a tax is placed on each unit of carbon emitted in Country X, the optimal tax level is 39.43. 

With the tax, Sector A will emit tons of carbon and abate tons. The benefit from emitting that amount of carbon is 6,506.22, and the cost of abatement is 1,282.61. The tax revenue generated from Sector A is 3,811.18.

With the tax, Sector B will emit tons of carbon and abate tons. The benefit from emitting that amount of carbon is 2,146.15, and the cost of abatement is 3,692.27. The tax revenue generated from Sector A is 1,912.36.

With the tax, Sector C will emit tons of carbon and abate tons. The benefit from emitting that amount of carbon is 15,499.57, and the cost of abatement is 904.93. The tax revenue generated from Sector A is 6,104.44.

The optimal tax level for a cabon tax policy was determined by horizontally aggregating the demand curves for each sector. The intersection of the aggregate demand with 300 total units of carbon emitted is the level of the optimal carbon tax. The intersection of that tax with the demand curve for each sector is the amount of carbon that will be emitted. The tax revenue generated is equal to the tax price multiplied by the number of units emitted by each sector. Again, the abatement cost is equal to the area under the abatement curve to the value of units abated by each sector (the difference between emissions with no tax and with the tax), and the benefit of emitting is the area under the demand curve over to the number of units emitted.

####3c. Cap and Trade

```{r, include = FALSE}
#3c 
#B will sell because they get the least benefit from emitting
#A and C will buy because they get more benefit from emitting
# C will buy the most because they have the highest benefit from emitting one more unit. 

trading_price <- tax

a_buys <- 80 - em_A_fn(tax)
#-16.66511 units

b_sells <- 100 - em_B_fn(trading_price)
#51.49558 units

c_buys <- 120 - em_C_fn(tax)
#-34.83047 units

c_loses <- -c_buys*tax
#1373.246 

b_gains <- b_sells*tax
#2030.294

a_loses <- -a_buys*tax
#657.0482 

polluted_units_A_cap <- polluted_units_A_tax
#96.66511 
polluted_units_B_cap <- polluted_units_B_tax
#48.50442
polluted_units_C_cap <- polluted_units_C_tax
#154.8305 

abated_units_A_cap <- (intercept_a - tax)/ -slope_a #abated units for sector A
#83.3348929655707 
abated_units_B_cap <- (intercept_b - tax)/ -slope_b #abated units for sector B
#151.495575967614 
abated_units_C_cap <- (intercept_c - tax)/ -slope_c #abated units for sector C
#65.169531066815 

# all values stay the same except for the trading units 
```

Under a cap and trade scenario, the trading price for carbon emissions will be 39.43. Sector A will pollute 96.67 tons, Sector B will pollute 48.5 tons, and Sector C will pollute 154.83 tons. Sector B will sell emission credits to both Sector A and Sector C, as the marginal cost of abatement for Sector C is the lowest. Sector A will buy 16.67 credits for 657.05 and Sector C will buy 34.83 units for 1,373.25. Sector B will sell 51.5 units and gain 2,030.29.

The carbon trading price in a cap and trade scenario is equal to the optimal tax level identified in 3b. From that price it was possible to calculate the optimal number of units of carbon that each sector will emit. The difference between that level and the permits assigned under cap and trade is the number of offsets that a sector will either buy or sell, depending on their marginal price of abatement. When the abatement cost is lower than the trading price, the sector will abate and sell the offset, and when the abatement cost is higher than the trading price, the sector will purchase an offset.

###4. Explore the inclusion of Country Y in the carbon market

```{r, include = FALSE}
#4

#aggregate emissions 
em_slope_ag_D <- em_slope_a+em_slope_b+em_slope_c + em_slope_d
em_int_ag_D <- em_int_a + em_int_b + em_int_c + em_int_d
em_ag_fn_D <- function(price){
  price*em_slope_ag_D + em_int_ag_D
  
}
price_slope_ag_D <- function(emissions){
  -em_int_ag_D/em_slope_ag_D + emissions/em_slope_ag_D
  
} 

tax_D <- price_slope_ag_D(600)

polluted_units_D_4 <- em_D_fn(tax_D)
#222.6131 
polluted_units_C_4 <- em_C_fn(tax_D) #polluted units for sector C
#167.1088
polluted_units_B_4 <- em_B_fn(tax_D) #polluted units for sector B
#96.92889 
polluted_units_A_4 <- em_A_fn(tax_D) #polluted units for sector A
#113.3492 

abated_units_A_tax_4 <- (intercept_a - tax_D)/ -slope_a #abated units for sector A
#66.65079 
abated_units_B_tax_4 <- (intercept_b - tax_D)/ -slope_b #abated units for sector B
#103.0711
abated_units_C_tax_4 <- (intercept_c - tax_D)/ -slope_c #abated units for sector C
#52.89119 
abated_units_D_tax_4 <- (intercept_d - tax_D)/ -slope_d #abated units for sector D
#77.3869

#Sector A
pollution_benefit_A_tax_4 <- polluted_units_A_4*tax_D + 0.5*polluted_units_A_4*(demand_a_int-tax_D)
#7083.733 
total_benefit_A_tax_4 <- integrate(demand_A_fn, 0 , 180)$value
abatement_cost_A_tax_4 <- total_benefit_A_tax_4 - pollution_benefit_A_tax_4
#705.0993 

#Sector B
pollution_benefit_B_tax_4 <- polluted_units_B_4*tax_D + 0.5*polluted_units_B_4*(demand_b_int-tax_D)
#2146.154
total_benefit_B_tax_4 <- integrate(demand_B_fn, 0 , 200)$value
abatement_cost_B_tax_4 <- total_benefit_B_tax_4 - pollution_benefit_B_tax_4
#2016.081 

##Sector C
pollution_benefit_C_tax_4 <- polluted_units_C_4*tax_D + 0.5*polluted_units_C_4*(demand_c_int-tax_D)
#15924.58 
total_benefit_C_tax_4 <- integrate(demand_C_fn, 0 , 220)$value
abatement_cost_C_tax_4 <- total_benefit_C_tax_4 - pollution_benefit_C_tax_4
#479.9205

#Sector D
pollution_benefit_D_tax_4 <- polluted_units_D_4*tax_D + 0.5*polluted_units_D_4*(demand_d_int-tax_D)
#13074.99 
total_benefit_D_tax_4 <- integrate(demand_D_fn, 0 , 300)$value
abatement_cost_D_tax_4 <- total_benefit_D_tax_4 - pollution_benefit_D_tax_4
#1528.004 

# Aggregated Costs and Benefits
abatement_cost_aggregated_tax <- abatement_cost_A_tax_4 + abatement_cost_B_tax_4 + abatement_cost_C_tax_4 + abatement_cost_D_tax_4 
#4729.105 

pollution_benefit_aggregated_tax <- pollution_benefit_A_tax_4 + pollution_benefit_B_tax_4 + pollution_benefit_C_tax_4 + pollution_benefit_D_tax_4
#39905.64 

# cap and trade
trading_price_4 <- tax_D
a_buys_4 <- 80 - em_A_fn(tax_D)
#-33.34921 
b_sells_4 <- 100 - em_B_fn(trading_price_4)
#3.071108 
c_buys_4 <- 120 - em_C_fn(tax_D)
#-47.10881  
d_sells <- 300 - em_D_fn(tax_D)
#77.3869
c_loses_4 <- -c_buys_4*tax_D
#1403.96 
b_gains_4 <- b_sells_4*tax_D
#91.52668 
a_loses_4 <- -a_buys_4*tax_D
#993.8895
d_gains_4 <- d_sells*tax_D
#2306.323
total_permit_rev_4 <- (d_gains_4 + b_gains_4) - (c_loses_4 + a_loses_4)
```

In a carbon market that includes both Country X and Country Y, both country's emissions would be capped at 300 tons and offsets could be traded between all 4 sectors. Sectors B and D would both sell offsets, and Sectors A and C would buy offsets.

The total cost of meeting these caps is 4,729.11 and the four sectors will benefit by 39,905.64 for being able to continue polluting to a certain extent. Sector A will emit 113.35 tons, Sector B will emit 96.93 tons, Sector C will emit 167.11 tons, and Sector D will emit 113.35 tons.

Sector A will buy 33.35 offsets for 993.89. Sector B will sell 3.07 offsets and make 91.53. Sector C will buy 47.11 offsets for 1,403.96, and Sector D will sell 77.39 offsets for 2,306.32.

Because Sector D in Country Y would enter the market and has a lower marginal price of abatement for early units of carbon emissions, Sector D will sell offset permits. This was determined by aggregating the emissions curves across all 4 sectors, setting the cap, and determining the trading price for carbon emissions.

###5. Every ton of carbon emissions creates 1 ton of local air pollution.

####a. Carbon cap and trade market for Country X only
Country X produces: 300 Tons of air pollution  

Country Y produces: 300 Tons of air pollution

####b. Country Y enters the carbon market with Country X
```{r, include = FALSE}
country_x_5b <- polluted_units_A_4 + polluted_units_B_4 + polluted_units_C_4
# 377.3869 
country_y_5b <- polluted_units_D_4
#222.6131 
```

If country Y enters the carbon market with Country X, Country X will have 377.39 units of air pollution and Country Y will have 222.61.


###c. 
Allowing cap and trade will lead to an increase in the tons of air pollution in country x and decrease it in country y.
