---
title: "ESM_204_Assignment_4"
author: "Bridget Gibbons, BR Hoover"
date: "6/3/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}

library(tidyverse)
library(janitor)
library(stargazer)

```


```{r, include=FALSE}

climate_raw <- read_csv("HW4Data.csv")

```

1. 

```{r, echo=FALSE}

lm_a <- lm(MC_A ~ Abatement, data = climate_raw)

lm_b <- lm(MC_B ~ Abatement, data = climate_raw)

lm_c <- lm(MC_C ~ Abatement, data = climate_raw)

lm_d <- lm(MC_D ~ Abatement, data = climate_raw)

summary(lm_a)
summary(lm_b)
summary(lm_c)
summary(lm_d)
```

```{r}

slope_a <- lm_a$coefficients[2]
slope_b <- lm_b$coefficients[2]
slope_c <- lm_c$coefficients[2]
slope_d <- lm_d$coefficients[2]

yint_a <- lm_a$coefficients[1]
yint_b <- lm_b$coefficients[1]
yint_c <- lm_c$coefficients[1]
yint_d <- lm_d$coefficients[1]
```


```{r}
all_model_plot <- ggplot(climate_raw, aes(x = Abatement)) +
  geom_smooth(aes(y = MC_A), method = lm, se = TRUE, size = 0.5, color = "red")+
  geom_smooth(aes(y = MC_B), method = lm, se = TRUE, size = 0.5, color = "green")+
  geom_smooth(aes(y = MC_C), method = lm, se = TRUE, size = 0.5, color = "blue")+
  geom_smooth(aes(y = MC_D), method = lm, se = TRUE, size = 0.5, color = "purple")+
  geom_point(aes(y = MC_A, color = "MC_A"))+
  geom_point(aes(y = MC_B, color = "MC_B"))+
  geom_point(aes(y = MC_C, color = "MC_C"))+
  geom_point(aes(y = MC_D, color = "MC_D"))

all_model_plot

```

As long as carbon credits are more expensive than this, they will abate

Sector A: MC_abatement = 0.57684x - 8.64448; A = 180
Sector B: MC_abatement = 9.31770 + 0.19874x; B= 200
Sector C: MC_abatement = 0.78383x - 11.65503; C = 220
Sector D: MC_abatement = 9.68751 + 0.25993x; D = 300

2. still need to graph these demand curves

Plugging in the quantities of current emissions to find MC of abatement for each sector, to find the intercept of the demand curve:

Sector A: MC_abatement = 0.57684(180) - 8.64448 -> 95.18672
Sector B: MC_abatement = 9.31770 + 0.19874(200); -> 49.0657
Sector C: MC_abatement = 0.78383(220) - 11.65503; -> 160.78757
Sector D: MC_abatement = 9.68751 + 0.25993(300); -> 87.66651

Then, use new y-intercept and x-intercept at full emissions levels to derive slope.

(0, 95.18672); (180, 0) -> slope = -0.5288151111
(0, 49.0657); (200, 0) -> slope = -0.2453285
(0, 160.78757); (220, 0) -> slope = -0.73085259
(0, 87.66651); (300, 0) -> slope = -0.2922217

```{r, echo=FALSE}
demand_slope_a <- -0.5288151111
demand_slope_b <- -0.2453285
demand_slope_c <- -0.73085259
demand_slope_d <- -0.2922217

demand_yint_a <- 95.18672
demand_yint_b <- 49.0657
demand_yint_c <- 160.78757
demand_yint_d <- 87.66651

```

Section A equation:

$$MC_A = 95.18672 - 0.5288151111(emissions) $$
$$MC_B = 49.0657 - 0.2453285(emissions)$$
$$MC_C = 160.78757 - 0.73085259(emissions)$$
$$MC_D = 87.66651 - 0.2922217(emissions)$$

Sector A is willing to pay 95.19 for first ton of emissions
Sector B is willing to pay 49.07 for first ton of emissions
Sector C is willing to pay 160.79 for first ton of emissions
Sector D is willing to pay 87.67 for first ton of emissions

Sector C is willing to pay the most for the first unit of carbon emissions.

3. Suppose to meet the Paris Accord commitments, country X needs to cut all carbon emissions in half.

a. Cap on carbon. Each sector (A, B, and C) must cut its carbon emissions by 100 tons (thus reducing total emissions from 600 down to 300).

```{r, include=FALSE}

abate<-c(100, 100, 100, 300)

MCa<-(demand_slope_a*100) + demand_yint_a 
MCb<-(demand_slope_b*100) + demand_yint_b
MCc<-(demand_slope_c*100) + demand_yint_c

MC<-rbind(MCa, MCb, MCc, NA)

costa<-(MCa*100)+(100*(demand_yint_a-MCa)*0.5)
costb<-(MCb*100)+(100*(demand_yint_b-MCb)*0.5)
costc<-(MCc*100)+(100*(demand_yint_c-MCc)*0.5)

totalcost<-sum(costa, costb, costc)

cost<-rbind(costa, costb, costc, totalcost)

part3_a<- cbind(abate, MC, cost)
colnames(part3_a)=c("Units abated","Marginal cost", "Cost")
row.names(part3_a)=c("Sector A", "Sector B", "Sector C", "Total Country X")

part3_a

```

There is no tax revenue because there is no tax.

b. Tax on carbon. To emit a ton of carbon in country X, you must pay a tax of $t. You will need to find the tax that accomplishes the desired reduction.

For sector a:
```{r}
#switch a slope and int to be in terms of q=
a_demand_int1 <- (-yint_a/slope_a)
a_demand_slope1 <- (1/slope_a)
a_demand1 <- function(x){a_demand_int1 + a_demand_slope1*x}
```

for sector b:
```{r}
#b slope and int to be in terms of q=
b_demand_int1 <- (-yint_b/slope_b)
b_demand_slope1 <- (1/slope_b)
b_demand1 <- function(x){b_demand_int1 + b_demand_slope1*x}
```

for sector c:
```{r}
#c slope and int to be in terms of q=
c_demand_int1 <- (-yint_c/slope_c)
c_demand_slope1 <- (1/slope_c)
c_demand1 <- function(x){c_demand_int1 + c_demand_slope1*x}
```

```{r}
#aggregate slope and intercept
agg_demand_int <- sum(a_demand_int1,b_demand_int1,c_demand_int1)
agg_demand_slope <- sum(a_demand_slope1, b_demand_slope1, c_demand_slope1)

#back in terms of p=
agg_demand_int1 <- (-agg_demand_int/agg_demand_slope)
agg_demand_slope1 <- (1/agg_demand_slope)
agg_demand_curve <- function(x){agg_demand_int1 + agg_demand_slope1*x}

optimal_tax <- agg_demand_curve(300)
```

```{r}
#emissions from sector A
a_emissions_tax <- a_demand1(optimal_tax)
#102.66 tons of CO2 

#cost of reduction for sector A

#emissions from sector B
b_emissions_tax <- b_demand1(optimal_tax)
#33.30

#cost of reduction for sector B
#original 

#emissions from sector C
c_emissions_tax <- c_demand1(optimal_tax)
#164.04

#cost of reduction for sector C

```


c. Cap and trade. Each sector (A, B, C) is allocated carbon permits equal to their current emissions minus 100 (same as in (a) above), thus achieving the total reduction of 300. Then, these three sectors are allowed to trade with each other. You will need to derive the outcome of that trading.

```{r}
#outcome of trading would result in the same amount of emissions as if a tax was imposed for each sector, the price of permits would be the same as the optimal tax

#only difference is the benefit of abatement = (100-emissions_tax)*optimal_tax

#benefit to A (will be a cost because they will end up emitting more than 100)
a_benefit_trade <- (100-a_emissions_tax)*optimal_tax
#-108.88

#benefit to B (because they will emit less than 100 and sell extra permits)
b_benefit_trade <- (100-b_emissions_tax)*optimal_tax
#2727.99

#benefit to C (will be a cost because they will end up emitting more than 1000)
c_benefit_trade <- (100-c_emissions_tax)*optimal_tax
#-2619.12

#all benefits go to B, because they have the lowest MC of abatement they can benefit most from abating and trading credits
```



4. Again, without any co-benefits, suppose that country Y (which only has one carbon-emitting sector, D) has no obligation to reduce its emissions. Country X asks country Y to enter the country X carbon market. Doing so would require country Y to put a cap on carbon emissions at its current level of emissions (300 tons), but would then allow country Y to sell carbon offsets to sectors A, B, or C. Are there any incentives for country Y to enter country X’s carbon market and to thus place a voluntary cap
on its emissions? Are there any incentives for country X to try to attract country Y into its market?

5. Now assume that every ton of carbon emissions creates 1 ton of local air pollution. Local air pollution causes economic damages (health, environmental, etc.), but only in the country in which it is emitted.
Assume there are no local air pollution regulations in either country X or country Y.

a. In a carbon cap and trade market that only covers sectors in country X, how much local air pollution would you expect in country X? In country Y?
b. If country Y enters the carbon market for country X (as in question 4 above), how much local pollution will there be in country X and country Y?
c. What advice can you give country X and country Y about the desirability of allowing international trade of carbon emissions credits?